---
title: ""
output: github_document
---

[![Travis-CI Build Status](https://travis-ci.com/SMAC-Group/ib.svg?branch=master)](https://travis-ci.com/github/SMAC-Group/ib)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-green.svg)](https://github.com/SMAC-Group/ib)
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bias correction via the iterative bootstrap

This is an under-development package that proposes the iterative bootstrap algorithm
of [Kuk (1995)](https://doi.org/10.1111/j.2517-6161.1995.tb02035.x)
and further studied by [Guerrier et al (2019)](https://doi.org/10.1080/01621459.2017.1380031)
and [Guerrier et al (2020)](https://arxiv.org/pdf/2002.08757.pdf).

In order to install the package
```{r, installation, eval = FALSE}
## if not installed
## install.packages("remotes")
remotes::install_github("SMAC-Group/ib")
```

The `ib` package is conceived as a wrapper: an `object` that needs a bias correction is supplied to the `ib()` function. For example, for a negative binomial regression:   

```{r, glm.nb, eval=FALSE}
library(ib)
library(MASS)
fit_nb <- glm.nb(Days ~ Sex/(Age + Eth*Lrn), data = quine)
fit_ib1 <- ib(fit_nb)
summary(fit_ib1)

## correct for overdispersion with H=100
fit_ib2 <- ib(fit_nb, control=list(H=100), extra_param = TRUE)
summary(fit_ib2)
```

By default, we support `object` which has a model call (`getCall(object)`), a design matrix (`model.matrix(object)`) and a `simulate()` method (see `help(simulate)`). 

We provide more parameters for which to correct the bias for `lm`, `glm`, `glm.nb`, `lmer` and `vglm` classes, as shown in the example above with the overdispersion parameter of the negative binomial regression. More details
are in `help(ib)`.

On top of `simulate`, we also consider cases where the response variable is generated using censoring, missing at random and outliers mechanisms (see
`help(ibControl)` for more details). For example

```{r, glm.nb with censoring, eval=FALSE}
## suppose values above 30 are censored
quine2 <- transform(quine, Days=pmin(Days,30))
fit_nb <- glm.nb(Days ~ Sex/(Age + Eth*Lrn), data = quine2)
fit_ib1 <- ib(fit_nb, control = list(cens=TRUE, right=30))
summary(fit_ib1)

## correct for overdispersion with H=100
fit_ib2 <- ib(fit_nb, control=list(H=100, cens=TRUE, right=30), extra_param = TRUE)
summary(fit_ib2)
```


